%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{DevOps Engineer}
{Ciox Health}
{Alpharetta, GA}
{June 2016 - Present}
{ % Description(s) of tasks/responsibilities
Create secure, automated software deployment pipelines using Jenkins for Microsoft and Java based web applications.
\begin{cvitems}
\item[]
\item {Automated the creation and configuration of Windows and RedHat virtual machines using Ansible, Jenkins, git, and VMware PowerCLI.}
\item {Host internal training for operations and engineering to integrate new tools such as Ansible and git.}
\item {Wrote Jenkins pipelines to scan Java applications for code style violations and security vulnerabilities.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Security Analyst}
{OpenSpan - Now Pegasystems}
{Alpharetta, GA}
{June 2015 - June 2016}
{ % Description(s) of tasks/responsibilities
Inspected security measures for the protection of Ruby-based, AWS-hosted web application and IT environments. Monitored and analyzed security controls, reviewed vulnerabilities, maintained and enforced security policies, and performed risk assessments.
\begin{cvitems}
\item[]
\item {Established vulnerability management program based on Tenable SecurityCenter.}
\item {Wrote policies and technical configuration documents to align with security standards and European privacy regulations.}
\item {Performed internal audits of cloud and IT infrastructure.}
\item {Drafted major components of the company's yearly risk assessment.}
\item {Created Ansible playbooks to bootstrap Ubuntu-based Vagrant environments.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Information Security Lead}
{Classic Graphics - division of Imagine{\it !} Print Solutions} % Organization
{Charlotte, NC} % Location
{May 2013 - March 2014} % Date(s)
 % Description(s) of tasks/responsibilities
{
Maintained the company's compliance with ISO 9001, ISO 27001, and PCI-DSS.
\begin{cvitems}
\item[]
\item {Coordinated the incident response lifecycle.}
\item {Co-managed the remediation of security audits, penetration tests, and vulnerability scans.}
\item {Delivered a compliance gap analyses to executive management.}
\item {Performed internal ISO 27001, PCI-DSS SAQ D audits.}
\item {Participated in a mock disasters with management.}
\item {Participated as a voting member in the Change Management Committee with respect to Information Security.}
\item {Proposed revisions to executive management for changes to internal documentation and policies.}
\item {Responded to sales-related information security questionnaires and RFP documents.}
\item {Evaluated security controls used to protect an in-house, VMWare-based cloud platform.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Senior Applications Architect}
{Classic Graphics} % Organization
{Charlotte, NC} % Location
{September 2007 - June 2015} % Date(s)
 % Description(s) of tasks/responsibilities
{
Maintained compliance with Fortune 500 customer project requirements. Provided technical leadership, guidance, and mentoring to the web application developers.
\begin{cvitems}
\item[]
\item {Determined which web application components and modules should be used for new web applications.}
\item {Ensured that secure, re-usable code and components were developed and incorporated into projects.}
\item {Took the lead in providing project estimates.}
\item {Developed specifications, prototypes, and initial user guides.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Development Manager}
{Classic Graphics} % Organization
{Charlotte, NC} % Location
{September 2010 - May 2013} % Date(s)
 % Description(s) of tasks/responsibilities
{
Achieved full continuous integration using Jenkins for an Ubuntu-based environment. Deployed web application code as it was completed, during business hours.
\begin{cvitems}
\item[]
\item {Automated deployments of code to come strictly from version control.}
\item {Maintained secure code scanning continuous integration and deployment workflows.}
\item {Trained developers on existing processes and web applications used for print manufacturing.}
\item {Formulated Classic-sponsored security modules into a security-focused Drupal distribution: Guardr.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{PHP Developer}
{Classic Graphics} % Organization
{Charlotte, NC} % Location
{September 2007 - September 2010} % Date(s)
 % Description(s) of tasks/responsibilities
{
Wrote and maintained a suite of web application security modules for compliance with policies regarding passwords, login security, inactive users, data sanitizing, activity log monitoring, site performance, and others.
}
%------------------------------------------------

\cventry
{Quality Rater}
{Workforcelogic}
{Telecommute}
{December 2006 - December 2007} % Date(s)
{ % Description(s) of tasks/responsibilities
1-year contract with Google to help train the Googlebot Pagerank engine to show timely and accurate results.
}

%------------------------------------------------

\cventry
{Information Technology Director}
{Advanced Automation Inc}
{Telecommute}
{August 2003 - June 2006} % Date(s)
{ % Description(s) of tasks/responsibilities
Collaborated with executives, sales, and support departments to develop a Drupal-based company intranet and a training extranet for hundreds of insurance agencies.
\begin{cvitems}
\item[]
\item {Managed server infrastructure for delivery of virtual sales meetings, dynamic web-based training, and interactive inter-agency information sharing.}
\item {Responsible for remotely diagnosing IT problems and making repairs. }
\item {Trained employees on new IT infrastructure as needed. }
\end{cvitems}
}

%------------------------------------------------

\cventry
{Computer Lab Assistant}
{The University of Texas at Tyler}
{Tyler, TX}
{February 2002 - June 2003} % Date(s)
{ % Description(s) of tasks/responsibilities
Responsible for operation of 3 campus computer labs.
\begin{cvitems}
\item[]
\item {Monitored and updated software on student email, Blackboard (web courseware), and Snort-based, OpenBSD network traffic monitoring servers.}
\item {Trained computer lab staff.}
\item {Performed hardware inventory audits.}
\item {Configured centralized antivirus updating and reports.}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Project Lead}
{Thatware PHP Weblog System}
{Telecommute}
{1999 - 2002} % Date(s)
{ % Description(s) of tasks/responsibilities
Thatware is open-source content management software. It is a Web-based news publishing and discussion backend written in PHP that can handle threaded discussions with a minimum of configuration and day-to-day management. Utilized PHP3, MySQL, FreeBSD, and Linux.
}

%------------------------------------------------

\cventry
{Senior Community Leader}
{Yahoo! Geocities}
{Telecommute}
{1998 - 1999} % Date(s)
{ % Description(s) of tasks/responsibilities
Managed geographically distributed volunteer staff responsible for increasing growth rate, retention of new users, and praise of quality content. Published weekly internal memo with notes on improving services. Handled terms of service violations.
}

%------------------------------------------------

\end{cventries}
